---
title: "PQHS C8Q9"
author: "Andrew Shan"
date: "April 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# (a) Create a training set containing a random sample of 800 observations, and a test set co?taining the remaining observations. 
```{r}
library(tidyverse)
library(ISLR)
attach(OJ)
set.seed(1)
train <- sample(1:nrow(OJ), 800)
OJ.train <- OJ[train, ]
OJ.test <- OJ[-train, ]
```

# (b) Fit a tree to the training data, with Purchase as the response a?d the other variables as predictors. Use the summary() function to produce summary statistics about the tree, and describe the results obtained. What is the training error rate? How many terminal nodes does the tree have? 

```{r}
library(tree)
tree.oj <- ?ree(Purchase ~ ., data = OJ.train)
summary(tree.oj)
```

The futted tree has 8 terminal notes abd a training error rate of 0.165.

#  Type in the name of the tree object in order to get a detailed text output. Pick one of the terminal nodes, and interpret ?he information displayed. 

```{r}
tree.oj
```

For the node labled 2. The splitting variables is LoyalCH, the criterion is LoyalCH < .508643, the number of observations in that branch is 350 with a deviance of 409 and overall predicition for the branch of?MM. About 27% points have CH as value of Sales and 73% have MM as value of Sales.

# (d) Create a plot of the tree, and interpret the results.
```{r}
plot(tree.oj)
text(tree.oj, pretty = 0)
```

The most important variable is LoyalCH. If LoyalCH>0.508643, ?he tree oreducts CH. 

# (e) Predict the response on the test data, and produce a confusion matrix comparing the test labels to the predicted test labels. What is the test error rate? 

```{r}
tree.pred <- predict(tree.oj, OJ.test, type = "class")
table(tr?e.pred, OJ.test$Purchase)
```

```{r}
(12+49)/(147+49+12+62)
```

The test error rate is about 22.59259%

# (f) Apply the cv.tree() function to the training set in order to determine the optimal tree size. 

```{r}
cv.oj <- cv.tree(tree.oj, FUN = prune.mis?lass)
cv.oj
```

# (g) Produce a plot with tree size on the x-axis and cross-validated classi???cation error rate on the y-axis. 

```{r}
plot(cv.oj$size, cv.oj$dev, type = "b", xlab = "Tree size", ylab = "Deviance")

```

# (h) Which tree size corresponds to the lowest cross-validated classi???cation error rate? 

The 2 node tree has lowest cross-validation error.

# (i) Produce a pruned tree corresponding to the optimal tree size obtained using cross-validation. If cross-validation does not lead to selection of a pruned tree, then create a prun?d tree with ???ve terminal nodes. 

```{r}
prune.oj <- prune.misclass(tree.oj, best = 2)
plot(prune.oj)
text(prune.oj, pretty = 0)
```

# (j) Compare the training error rates between the pruned and unpruned trees. Which is higher? 
```{r}
summary(tree.oj)
summary(prune.o?)
```

The pruned tree has a higher misclassfication error rate. 

# (k) Compare the test error rates between the pruned and unpruned trees. Which is higher?

```{r}
prune.pred <- predict(prune.oj, OJ.test, type = "class")
table(prune.pred, OJ.test$Purchas?)
```

```{r}
(40+30)/(119+81+70)
```

The error increased to 25.93% .